Independent discovery of a nulling pulsar with unusual sub-pulse drifting properties with the Murchison Widefield Array

### 2022-05-29 paper/main.tex
Removed the boldface to indicate changes from the previous round

Pulsars are rapidly rotating neutron stars, the sites of some of the highest energy physical processes in the universe, owing to the very strong gravitational and magnetic fields that surround them.
Discovered first via their lighthouse-like beam of radio emission \citep{Hewish1968}, which we detect as a series of regularly spaced pulses, it was quickly realised that the physics governing the relativistic plasma that generates this beam was not well understood---a state of affairs that persists to the present day \citep[e.g.][]{Melrose2021}.
The uniqueness of each pulsar's emission signature provides a wealth of information that can be used to test proposed emission mechanisms, and it has been proven again and again over the past several decades that in-depth studies of individual pulsars can provide valuable clues for understanding the population as a whole.
{\bf
This, along with tests of general relativity \citep[e.g.][]{Kramer2006,Miao2021}, pulsar timing arrays for gravitational wave detection \citep[e.g.][]{Manchester2013}, pulsar braking and magnetospheric dynamics \citep[e.g.][]{Gao2017,Wang2020}, the neutron star equation of state \citep[e.g.][]{Demorest2010,Antoniadis2013,Pang2021}, and other pulsar science applications, motivates efforts to find new pulsars via large scale pulsar surveys, which continue to be conducted up to the present day.
}

@@

Many sub-pulse drifters, e.g., B0809$+$74 and B0943$+$10, are known to have very stable drift rates \citep[e.g.][]{Taylor1971,Deshpande1999}.
This stability partly motivated the original carousel model, put forward by \citet{Ruderman1975}, which associates the sub-pulses with spatially discrete bursts of electrical discharges (``sparks'') in regions of charge depletion just above the stellar surface near the magnetic poles.
According to this model, the sparks are driven by \ExB{} drift, with the observed stability of the drift rate being directly inherited from the theoretical stability of the electric and magnetic fields at the spark locations.
Therefore, pulsars that exhibit anything more complicated than a single, stable drift rate deserve special attention, since they require modifications of, or at least extensions to, the basic carousel model.
{\bf
Such pulsars exist, and several extensions have been proposed over the years to account for them.
For example, \citet{Gil2000} suggest that a quasi-central spark can account for (non-drifting) core components in profiles, and the well-known phenomenon of bi-drifting may be explained by presence of an inner annular gap \citep{Qiao2004}, an inner acceleration gap \citep{Basu2020}, or non-circular spark motions \citep{Wright2017}.
Such extensions are typically developed to explain specific drifting behaviors that are observed in a relatively small subset of pulsars, and there still lacks a single, comprehensive theory that can describe all drifting behaviors.
}

{\bf
Pulsars that both show complicated drifting behavior and are bright enough for single pulse analysis, are relatively rare.
}
Even a cursory glance at the drift bands of \psr{} show that its drifting behavior is indeed complex and bright, making it a welcome addition to this category of pulsar.
{\bf 
\psr{} is also found to contain null sequences, a phenomenon which is known to be connected to sub-pulse drifting, originally noticed by \citet{Lyne1983}, and further attested by recent studies of PSRs J1727$-$2739 \citep{Wen2016}, B1819$-$22 \citep{Janagal2022}, and the Vela pulsar \citep{Wen2020}.
}

@@

\begin{deluxetable}{ccccc}
\tabletypesize{\scriptsize}
\tablewidth{0pt}
    \tablecaption{MWA Observations of PSR \psr{} \label{tab:observations}}
\tablehead{
\colhead{MJD} & \colhead{Obs ID} & \multicolumn{2}{c}{Number of rotations} \\
& & Total & With detectable emission
}
\startdata
58434 & 1226062160 & 3759 & 788 \\
58991 & 1274143152 & 914  & 358 \\
{\bf 59002} & 1275094456 & 917  &  10 \\
{\bf 59002} & 1275172216 & 917  &  16 \\
59003 & 1275178816 & 914  & 281 \\
59094 & 1283104232 & 1374 & 545
\enddata
\tablecomments{All observations are in the $140$-$170\,$MHz band, with $100\,\mu$s/$10\,$kHz resolutions.}
\end{deluxetable}

Each observation was individually calibrated using {\bf observations of 3C444 taken within $\sim2$ hours of the respective target observations.
The calibration solutions were obtained using} the Real Time System software \citep{Mitchell2008}.
After calibration, the voltages were used to form a tied-array beam in the direction of the pulsar (the localization procedure is discussed in \S\ref{sec:localization}), using the bespoke beamforming software described in \citet{Ord2019}.
{\bf The MWA is located in a very radio quiet location, and no significant radio frequency interference was found in the beamformed data.}
After determining the best dispersion measure (DM) and period (see \S\ref{sec:period}), de-dispersion and folding were performed with {\tt DSPSR} \citep{VanStraten2011b} and {\tt PSRCHIVE} \citep{Hotan2004} to form single pulse archives, from which Stokes I pulse stacks were created.
Profiles of each detection, as well as an integrated profile incorporating the data from all four observations, is shown in Fig \ref{fig:profiles}.
Subsequent analysis of the pulse stacks is described in \S\ref{sec:analysis}.
\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{profiles.png}
    \caption{{\bf Peak-normalised mean profiles (black) of four of the observations}, and the total mean profile (top panel) including all four observations, with a time resolution of $\sim1.3\,$ms. {\bf The two observations on MJD 59002 are not included here as they consist almost entirely of noise.} The profiles show a barely resolved double peak structure. {\bf The gray lines show the profiles made up only of pulses classified as nulls.}}
    \label{fig:profiles}
\end{figure}

@@

Follow-up of the initial MWA detection with the full 80 minutes, as well as in other archival MWA observations, revealed that the pulsar has a very large nulling fraction ($\sim$~\nullfraction{})\footnote{The nulling fraction estimate comes only from analysis of the MWA observations.}, with some nulling sequences {\bf (excluding occasional intermittent pulses) potentially exceeding $20\,$min (i.e. the length of the first observation on MJD 59002, which contained \textit{only} a few intermittent pulses, as shown in Fig. \ref{fig:maxima})}.
A full analysis of the nulling properties is presented in Section \S\ref{sec:nulling} below.
Despite the fact that \psr{} was serendipitously discovered in the first ten minutes, it may well be the harbinger for a population of relatively bright, intermittent pulsars which the SMART survey, with its $80$-minute dwell times, is well-suited to detect.
A similar strategy is employed in the Low Frequency Array (LOFAR) Tied-Array All-Sky Survey \citep[LOTAAS;][]{Sanidas2019} and the low latitude ($|b| \le 5^\circ$) segment of the High Time Resolution Universe survey \citep[HTRU;][]{Keith2010}, which use dwell times of approximately one hour.

@@

The other {\bf five observations} were taken when the MWA was in its extended configuration, giving a tied-array beam size of $\sim3^\prime$ at $155\,$MHz.
Localization within {\bf the four observations in which the pulsar was bright enough} followed the identical procedure as used in \citet{Swainston2021}, i.e.\ gridding the candidate positions with overlapping tied-array beams and using signal-to-noise and the estimated beam shape to produce a likelihood map of the source position.
It is known that the ionosphere is capable of shifting the apparent position of sources by an appreciable fraction ($\sim10$-$30\%$) of the tied-array beam, and that these offsets are not necessarily corrected by the calibration process when the calibration observations are separated from the target observation, both spatially and temporally \citep{Swainston2022}.
Nevertheless, the localization afforded by the extended array observations was sufficiently precise (a few arcminutes) to warrant follow-up with a high-resolution imaging telescope.
Accordingly, images made with Band 3 ($300$-$500\,$MHz) data from the upgraded Giant Metrewave Radio Telescope \citep[uGMRT;][]{Gupta2017}, obtained under Director's Discretionary Time (DDTC185), enabled us to confirm the pulsar's position to an accuracy of $\sim1^\prime$.
The right ascension and declination of the final best position, consistent with both the uGMRT imaging and the MWA extended configuration observations, are {\bf 00h26m36s and $-$19$^\circ$55'59''}.

@@

Lacking a timing solution, we used PSRCHIVE's \texttt{pdmp} routine to determine the best period ($P$) and DM for each observation independently. {\bf This routine performs a brute-force grid search in both period and DM parameter space, and returns the period and DM that yields the highest profile signal-to-noise}. The weighted averages {\bf of both period and DM (respectively)} over the four observations were calculated, {\bf with the uncertainties reported by \texttt{pdmp} being} used to weight the individual measurements.
The values thus derived were $P = 1.306150 \pm 0.000005\,$s and $\text{DM} = \psrdm \pm \psrdmerr\,$\dmunit.
This simple estimate does not take the period derivative into account (in fact, it implicitly assumes $\dot{P} = 0$), and we note that a sufficiently large $\dot{P}$ would cause the period to drift significantly over the time period spanned by our four MWA observations ($\sim1.5\,$yr).
However, the pulse stacks (e.g.\ Fig. \ref{fig:pulsestacks}) folded on the above period showed no detectable slope, which we estimate would be discernible if the pulse window changed by more than $20\,$ms over the course of the observation.
Given this, we place a conservative upper limit of $|\dot{P}| \le 10^{-13}$\,s\,s$^{-1}$.

@@

\begin{figure*}[t]
    \includegraphics[width=\textwidth]{maxima_plot.png}
    \caption{Peak flux density within the pulse window as a function of time for six MWA observations (MJDs given along the $y$-axis). {\bf The shaded gray regions show detected subpulses that are included in the nulling fraction estimation, as explained in the text.} The peak fluxes were measured after smoothing the time series with a Gaussian filter ($\sim2\,$ms wide, the approximate width of a sub-pulse) to suppress the noise contribution and accentuate the contrast between nulling and burst sequences. {\bf Note that the low-level peaks in the $\sim70$-$80\,$mins time range of the MJD 58434 and in the second MJD 59002 observation} are single pulses faintly visible in the pulse stack, but which are faint because the pulsar was moving out of the MWA's primary beam.}
    \label{fig:maxima}
\end{figure*}

To estimate the nulling fraction, we first identified which pulses contained sub-pulses within the pulse window (this is a semi-automated procedure described in \S\ref{sec:drifting_analysis}).
Any pulse without a sub-pulse is then counted as a null, even if it is nested within a burst sequence.
{\bf Under this definition, we report a nulling fraction of $\sim$~\nullfraction{}.}

This working definition of a null may misclassify pulses with broad emission spread out over the pulse window, even if its integrated flux density is statistically significant.
{\bf For comparison, we present the pulse energy histograms of both on- and off-pulse regions of the pulse stacks for each of the six observations in Fig. \ref{fig:nullhist}.
The similarity between the on- and off pulse distributions for observations 1275094456 and 1275172216 indicate that any broad emission that is present falls well below the MWA detection threshold.
Despite this}, the uncertainty in our estimate of the nulling fraction will still be dominated by the lack of a statistically significant number of burst sequences.

\begin{figure*}[p]
    \centering
    \includegraphics[width=0.48\textwidth]{1226062160_nullhist.png}
    \includegraphics[width=0.48\textwidth]{1274143152_nullhist.png} \\
    \includegraphics[width=0.48\textwidth]{1275094456_nullhist.png}
    \includegraphics[width=0.48\textwidth]{1275172216_nullhist.png} \\
    \includegraphics[width=0.48\textwidth]{1275178816_nullhist.png}
    \includegraphics[width=0.48\textwidth]{1283104232_nullhist.png}
    \caption{{\bf The pulse energy histograms for each of the six observations, for matched-size on- and off-pulse regions of the pulse stacks. The ObsIDs are given above each plot. The on-pulse histograms include all pulses, regardless of whether they were classified as nulls by the method described in the text.}}
    \label{fig:nullhist}
\end{figure*}

@@

Fig. \ref{fig:with_model} shows the result of the drift band fitting to the MJD 58991 observation, alongside the values of $P_2$, $P_3$, and the drift rate predicted by the model.
\begin{figure*}[!tp]
    \centering
    \includegraphics[width=\textwidth]{1274143152_with_model.png}
    \caption{\textbf{Left:} The pulse stack of MJD 58991 (right panel of Fig \ref{fig:pulsestacks}), with the drift bands modelled with an exponentially decaying drift rate. \textbf{Right:} The $P_2$, instantaneous $P_3$, and instantaneous drift rates derived from the model. In the $P_2$ panel, the vertical error bars indicate the error on the fitted $P_2$ value, and the horizontal error bars only indicate the extent of the associated drift sequence.}
    \label{fig:with_model}
\end{figure*}
One can immediately note several interesting features.
First, the modelling bears out the observation that $P_3$ can indeed change gradually over the course of the mode A drift sequences by a large amount, even by more than a factor of two (from $\sim20$ to $40\,P$ in one case).
Second, $P_2$ appears to be generally smaller for mode B sequences ($\sim12^\circ$) than mode A ($\sim14^\circ$).
Whether or not this is true generally, or whether a single value of $P_2$ could be used to model all drift sequences simultaneously has not been attempted here, but in any case would require a larger sample of drift sequences to test robustly.

@@

Fluctuation spectra are most useful when the drift bands are regularly spaced (i.e.\ when $P_3$ is constant).
The fact that this is clearly not the case for \psr{} means that features in the fluctuation spectra will be spread out over a range of spectral bins.
Fig. \ref{fig:lrfs} shows the longitude-resolved fluctuation spectrum (LRFS) and the two-dimensional fluctuation spectrum (2DFS) for the drift sequence shown in Fig. \ref{fig:A2_example}.
\begin{figure}[t]
    \centering
    \includegraphics[width=0.45\textwidth]{A2_lrfs.png} \\
    \includegraphics[width=0.45\textwidth]{A2_tdfs.png}
    \caption{\textit{Top:} The LRFS computed on the section of the pulsestack shown in Fig. \ref{fig:A2_example}. \textit{Bottom:} A zoomed section of the 2DFS of the same pulse stack section. {\bf The feature at $\sim0.03\,$cycles/$P$ corresponds to $P_3 \approx 33 \pm 4\,P$, consistent with the average $P_3$ of this sequence determined from the pulse stack directly. The more diffuse power in the range $0.05$-$0.1\,$cycles/$P$ in the leading component (and the corresponding feature visible in the 2DFS) are indicative of the relative disorganization of the drift bands that occurs there.}}
    \label{fig:lrfs}
\end{figure}
Despite the changing $P_3$ and the relative disorganization of the drift rate, the LRFS and 2DFS show surprisingly high-Q features at $P_3 \approx 33 \pm 4\,P$ and $P_2 \approx 16^\circ \pm 2^\circ$, which are consistent with the fitted model values of $P_3$ changing from $\sim50\,P$ to $27\,P$ throughout the sequence, and $P_2 = 13.8^\circ \pm 0.3^\circ$.
The relative lack of power in the {\bf bottom panel of the LRFS} near phase $\sim2^\circ$ is likely related to the interruptions in the organization of the drift bands that occur at that phase, discussed in the previous section.
{\bf Interestingly, the presence of extra power in the LRFS in the leading component between $0.05$-$0.1\,$cycles/$P$ is suggestive of a connection to Mode B, which (with its $P_3 \approx 10\,P$) would be expected to contribute power in the LRFS near this range.}

@@

All of these complex drifting behaviors present a natural challenge to the carousel model, whose most basic formulation predicts only a single stable drifting mode, due to the expected stability of the underlying electric and magnetic fields that generate the carousel motion.
Nevertheless, many of the above effects can be successfully explained with the carousel model by invoking aliasing effects that arise due to beating between the stellar rotation rate and the carousel's rotation.
In the presence of aliasing, multiple drift modes can be explained if the number of sparks in the carousel changes, even if the carousel speed itself doesn't change.
This idea has been invoked to explain the multiple drift rates of B1918$+$19 \citep{Rankin2013}, B1819$-$22 \citep{Joshi2017,Janagal2022}, and B0031$-$07 \citep{McSweeney2019a}.
Aliasing can also ``amplify'' the variability of the drift rate if the ratio of stellar rotation and carousel rotation is very close to a ratio of small integers.
That is, a small change in the magnetospheric conditions {\bf (e.g. the local electromagnetic configuration)} near the stellar surface ({\bf in the gap,} where the sparks reside) can appear to the observer as a relatively large change in the drift rate.
\citet{VanLeeuwen2012} elucidated the connection between the accelerating potential within the polar gap and the carousel behavior, and found that the variability of B0826$-$34's drift rate can be explained in this way.
{\bf In contrast, \citet{VanLeeuwen2003} argued that aliasing could \emph{not} be present during the post-null changing drift rate for B0809$+$74.
Whether or not aliasing is included, models for changing drift rates are often discussed in terms of the local magnetospheric conditions changing over the relevant time scales \citep[e.g.][]{VanLeeuwen2003, Yuen2019}.}

>>>>

Pulsars are rapidly rotating neutron stars, the sites of some of the highest energy physical processes in the universe, owing to the very strong gravitational and magnetic fields that surround them.
Discovered first via their lighthouse-like beam of radio emission \citep{Hewish1968}, which we detect as a series of regularly spaced pulses, it was quickly realised that the physics governing the relativistic plasma that generates this beam was not well understood---a state of affairs that persists to the present day \citep[e.g.][]{Melrose2021}.
The uniqueness of each pulsar's emission signature provides a wealth of information that can be used to test proposed emission mechanisms, and it has been proven again and again over the past several decades that in-depth studies of individual pulsars can provide valuable clues for understanding the population as a whole.
This, along with tests of general relativity \citep[e.g.][]{Kramer2006,Miao2021}, pulsar timing arrays for gravitational wave detection \citep[e.g.][]{Manchester2013}, pulsar braking and magnetospheric dynamics \citep[e.g.][]{Gao2017,Wang2020}, the neutron star equation of state \citep[e.g.][]{Demorest2010,Antoniadis2013,Pang2021}, and other pulsar science applications, motivates efforts to find new pulsars via large scale pulsar surveys, which continue to be conducted up to the present day.

@@

Many sub-pulse drifters, e.g., B0809$+$74 and B0943$+$10, are known to have very stable drift rates \citep[e.g.][]{Taylor1971,Deshpande1999}.
This stability partly motivated the original carousel model, put forward by \citet{Ruderman1975}, which associates the sub-pulses with spatially discrete bursts of electrical discharges (``sparks'') in regions of charge depletion just above the stellar surface near the magnetic poles.
According to this model, the sparks are driven by \ExB{} drift, with the observed stability of the drift rate being directly inherited from the theoretical stability of the electric and magnetic fields at the spark locations.
Therefore, pulsars that exhibit anything more complicated than a single, stable drift rate deserve special attention, since they require modifications of, or at least extensions to, the basic carousel model.
Such pulsars exist, and several extensions have been proposed over the years to account for them.
For example, \citet{Gil2000} suggest that a quasi-central spark can account for (non-drifting) core components in profiles, and the well-known phenomenon of bi-drifting may be explained by presence of an inner annular gap \citep{Qiao2004}, an inner acceleration gap \citep{Basu2020}, or non-circular spark motions \citep{Wright2017}.
Such extensions are typically developed to explain specific drifting behaviors that are observed in a relatively small subset of pulsars, and there still lacks a single, comprehensive theory that can describe all drifting behaviors.

Pulsars that both show complicated drifting behavior and are bright enough for single pulse analysis, are relatively rare.
Even a cursory glance at the drift bands of \psr{} show that its drifting behavior is indeed complex and bright, making it a welcome addition to this category of pulsar.
\psr{} is also found to contain null sequences, a phenomenon which is known to be connected to sub-pulse drifting, originally noticed by \citet{Lyne1983}, and further attested by recent studies of PSRs J1727$-$2739 \citep{Wen2016}, B1819$-$22 \citep{Janagal2022}, and the Vela pulsar \citep{Wen2020}.

@@

\begin{deluxetable}{ccccc}
\tabletypesize{\scriptsize}
\tablewidth{0pt}
    \tablecaption{MWA Observations of PSR \psr{} \label{tab:observations}}
\tablehead{
\colhead{MJD} & \colhead{Obs ID} & \multicolumn{2}{c}{Number of rotations} \\
& & Total & With detectable emission
}
\startdata
58434 & 1226062160 & 3759 & 788 \\
58991 & 1274143152 & 914  & 358 \\
59002 & 1275094456 & 917  &  10 \\
59002 & 1275172216 & 917  &  16 \\
59003 & 1275178816 & 914  & 281 \\
59094 & 1283104232 & 1374 & 545
\enddata
\tablecomments{All observations are in the $140$-$170\,$MHz band, with $100\,\mu$s/$10\,$kHz resolutions.}
\end{deluxetable}

Each observation was individually calibrated using observations of 3C444 taken within $\sim2$ hours of the respective target observations.
The calibration solutions were obtained using the Real Time System software \citep{Mitchell2008}.
After calibration, the voltages were used to form a tied-array beam in the direction of the pulsar (the localization procedure is discussed in \S\ref{sec:localization}), using the bespoke beamforming software described in \citet{Ord2019}.
The MWA is located in a very radio quiet location, and no significant radio frequency interference was found in the beamformed data.
After determining the best dispersion measure (DM) and period (see \S\ref{sec:period}), de-dispersion and folding were performed with {\tt DSPSR} \citep{VanStraten2011b} and {\tt PSRCHIVE} \citep{Hotan2004} to form single pulse archives, from which Stokes I pulse stacks were created.
Profiles of each detection, as well as an integrated profile incorporating the data from all four observations, is shown in Fig \ref{fig:profiles}.
Subsequent analysis of the pulse stacks is described in \S\ref{sec:analysis}.
\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{profiles.png}
    \caption{Peak-normalised mean profiles (black) of four of the observations, and the total mean profile (top panel) including all four observations, with a time resolution of $\sim1.3\,$ms. The two observations on MJD 59002 are not included here as they consist almost entirely of noise. The profiles show a barely resolved double peak structure. The gray lines show the profiles made up only of pulses classified as nulls.}
    \label{fig:profiles}
\end{figure}

@@

Follow-up of the initial MWA detection with the full 80 minutes, as well as in other archival MWA observations, revealed that the pulsar has a very large nulling fraction ($\sim$~\nullfraction{})\footnote{The nulling fraction estimate comes only from analysis of the MWA observations.}, with some nulling sequences (excluding occasional intermittent pulses) potentially exceeding $20\,$min (i.e. the length of the first observation on MJD 59002, which contained \textit{only} a few intermittent pulses, as shown in Fig. \ref{fig:maxima}).
A full analysis of the nulling properties is presented in Section \S\ref{sec:nulling} below.
Despite the fact that \psr{} was serendipitously discovered in the first ten minutes, it may well be the harbinger for a population of relatively bright, intermittent pulsars which the SMART survey, with its $80$-minute dwell times, is well-suited to detect.
A similar strategy is employed in the Low Frequency Array (LOFAR) Tied-Array All-Sky Survey \citep[LOTAAS;][]{Sanidas2019} and the low latitude ($|b| \le 5^\circ$) segment of the High Time Resolution Universe survey \citep[HTRU;][]{Keith2010}, which use dwell times of approximately one hour.

@@

The other five observations were taken when the MWA was in its extended configuration, giving a tied-array beam size of $\sim3^\prime$ at $155\,$MHz.
Localization within the four observations in which the pulsar was bright enough followed the identical procedure as used in \citet{Swainston2021}, i.e.\ gridding the candidate positions with overlapping tied-array beams and using signal-to-noise and the estimated beam shape to produce a likelihood map of the source position.
It is known that the ionosphere is capable of shifting the apparent position of sources by an appreciable fraction ($\sim10$-$30\%$) of the tied-array beam, and that these offsets are not necessarily corrected by the calibration process when the calibration observations are separated from the target observation, both spatially and temporally \citep{Swainston2022}.
Nevertheless, the localization afforded by the extended array observations was sufficiently precise (a few arcminutes) to warrant follow-up with a high-resolution imaging telescope.
Accordingly, images made with Band 3 ($300$-$500\,$MHz) data from the upgraded Giant Metrewave Radio Telescope \citep[uGMRT;][]{Gupta2017}, obtained under Director's Discretionary Time (DDTC185), enabled us to confirm the pulsar's position to an accuracy of $\sim1^\prime$.
The right ascension and declination of the final best position, consistent with both the uGMRT imaging and the MWA extended configuration observations, are 00h26m36s and $-$19$^\circ$55'59''.

@@

Lacking a timing solution, we used PSRCHIVE's \texttt{pdmp} routine to determine the best period ($P$) and DM for each observation independently. This routine performs a brute-force grid search in both period and DM parameter space, and returns the period and DM that yields the highest profile signal-to-noise. The weighted averages of both period and DM (respectively) over the four observations were calculated, with the uncertainties reported by \texttt{pdmp} being used to weight the individual measurements.
The values thus derived were $P = 1.306150 \pm 0.000005\,$s and $\text{DM} = \psrdm \pm \psrdmerr\,$\dmunit.
This simple estimate does not take the period derivative into account (in fact, it implicitly assumes $\dot{P} = 0$), and we note that a sufficiently large $\dot{P}$ would cause the period to drift significantly over the time period spanned by our four MWA observations ($\sim1.5\,$yr).
However, the pulse stacks (e.g.\ Fig. \ref{fig:pulsestacks}) folded on the above period showed no detectable slope, which we estimate would be discernible if the pulse window changed by more than $20\,$ms over the course of the observation.
Given this, we place a conservative upper limit of $|\dot{P}| \le 10^{-13}$\,s\,s$^{-1}$.

@@

\begin{figure*}[t]
    \includegraphics[width=\textwidth]{maxima_plot.png}
    \caption{Peak flux density within the pulse window as a function of time for six MWA observations (MJDs given along the $y$-axis). The shaded gray regions show detected subpulses that are included in the nulling fraction estimation, as explained in the text. The peak fluxes were measured after smoothing the time series with a Gaussian filter ($\sim2\,$ms wide, the approximate width of a sub-pulse) to suppress the noise contribution and accentuate the contrast between nulling and burst sequences. Note that the low-level peaks in the $\sim70$-$80\,$mins time range of the MJD 58434 and in the second MJD 59002 observation are single pulses faintly visible in the pulse stack, but which are faint because the pulsar was moving out of the MWA's primary beam.}
    \label{fig:maxima}
\end{figure*}

To estimate the nulling fraction, we first identified which pulses contained sub-pulses within the pulse window (this is a semi-automated procedure described in \S\ref{sec:drifting_analysis}).
Any pulse without a sub-pulse is then counted as a null, even if it is nested within a burst sequence.
Under this definition, we report a nulling fraction of $\sim$~\nullfraction{}.

This working definition of a null may misclassify pulses with broad emission spread out over the pulse window, even if its integrated flux density is statistically significant.
For comparison, we present the pulse energy histograms of both on- and off-pulse regions of the pulse stacks for each of the six observations in Fig. \ref{fig:nullhist}.
The similarity between the on- and off pulse distributions for observations 1275094456 and 1275172216 indicate that any broad emission that is present falls well below the MWA detection threshold.
Despite this, the uncertainty in our estimate of the nulling fraction will still be dominated by the lack of a statistically significant number of burst sequences.

\begin{figure*}[p]
    \centering
    \includegraphics[width=0.48\textwidth]{1226062160_nullhist.png}
    \includegraphics[width=0.48\textwidth]{1274143152_nullhist.png} \\
    \includegraphics[width=0.48\textwidth]{1275094456_nullhist.png}
    \includegraphics[width=0.48\textwidth]{1275172216_nullhist.png} \\
    \includegraphics[width=0.48\textwidth]{1275178816_nullhist.png}
    \includegraphics[width=0.48\textwidth]{1283104232_nullhist.png}
    \caption{The pulse energy histograms for each of the six observations, for matched-size on- and off-pulse regions of the pulse stacks. The ObsIDs are given above each plot. The on-pulse histograms include all pulses, regardless of whether they were classified as nulls by the method described in the text.}
    \label{fig:nullhist}
\end{figure*}

@@

Fig. \ref{fig:with_model} shows the result of the drift band fitting to the MJD 58991 observation, alongside the values of $P_2$, $P_3$, and the drift rate predicted by the model.
\begin{figure*}[!tp]
    \centering
    \includegraphics[width=\textwidth]{1274143152_with_model.png}
    \caption{\textit{Left:} The pulse stack of MJD 58991 (right panel of Fig \ref{fig:pulsestacks}), with the drift bands modelled with an exponentially decaying drift rate. \textit{Right:} The $P_2$, instantaneous $P_3$, and instantaneous drift rates derived from the model. In the $P_2$ panel, the vertical error bars indicate the error on the fitted $P_2$ value, and the horizontal error bars only indicate the extent of the associated drift sequence.}
    \label{fig:with_model}
\end{figure*}
One can immediately note several interesting features.
First, the modelling bears out the observation that $P_3$ can indeed change gradually over the course of the mode A drift sequences by a large amount, even by more than a factor of two (from $\sim20$ to $40\,P$ in one case).
Second, $P_2$ appears to be generally smaller for mode B sequences ($\sim12^\circ$) than mode A ($\sim14^\circ$).
Whether or not this is true generally, or whether a single value of $P_2$ could be used to model all drift sequences simultaneously has not been attempted here, but in any case would require a larger sample of drift sequences to test robustly.

@@

Fluctuation spectra are most useful when the drift bands are regularly spaced (i.e.\ when $P_3$ is constant).
The fact that this is clearly not the case for \psr{} means that features in the fluctuation spectra will be spread out over a range of spectral bins.
Fig. \ref{fig:lrfs} shows the longitude-resolved fluctuation spectrum (LRFS) and the two-dimensional fluctuation spectrum (2DFS) for the drift sequence shown in Fig. \ref{fig:A2_example}.
\begin{figure}[t]
    \centering
    \includegraphics[width=0.45\textwidth]{A2_lrfs.png} \\
    \includegraphics[width=0.45\textwidth]{A2_tdfs.png}
    \caption{\textit{Top:} The LRFS computed on the section of the pulsestack shown in Fig. \ref{fig:A2_example}. \textit{Bottom:} A zoomed section of the 2DFS of the same pulse stack section. The feature at $\sim0.03\,$cycles/$P$ corresponds to $P_3 \approx 33 \pm 4\,P$, consistent with the average $P_3$ of this sequence determined from the pulse stack directly. The more diffuse power in the range $0.05$-$0.1\,$cycles/$P$ in the leading component (and the corresponding feature visible in the 2DFS) are indicative of the relative disorganization of the drift bands that occurs there.}
    \label{fig:lrfs}
\end{figure}
Despite the changing $P_3$ and the relative disorganization of the drift rate, the LRFS and 2DFS show surprisingly high-Q features at $P_3 \approx 33 \pm 4\,P$ and $P_2 \approx 16^\circ \pm 2^\circ$, which are consistent with the fitted model values of $P_3$ changing from $\sim50\,P$ to $27\,P$ throughout the sequence, and $P_2 = 13.8^\circ \pm 0.3^\circ$.
The relative lack of power in the bottom panel of the LRFS near phase $\sim2^\circ$ is likely related to the interruptions in the organization of the drift bands that occur at that phase, discussed in the previous section.
Interestingly, the presence of extra power in the LRFS in the leading component between $0.05$-$0.1\,$cycles/$P$ is suggestive of a connection to Mode B, which (with its $P_3 \approx 10\,P$) would be expected to contribute power in the LRFS near this range.

@@

All of these complex drifting behaviors present a natural challenge to the carousel model, whose most basic formulation predicts only a single stable drifting mode, due to the expected stability of the underlying electric and magnetic fields that generate the carousel motion.
Nevertheless, many of the above effects can be successfully explained with the carousel model by invoking aliasing effects that arise due to beating between the stellar rotation rate and the carousel's rotation.
In the presence of aliasing, multiple drift modes can be explained if the number of sparks in the carousel changes, even if the carousel speed itself doesn't change.
This idea has been invoked to explain the multiple drift rates of B1918$+$19 \citep{Rankin2013}, B1819$-$22 \citep{Joshi2017,Janagal2022}, and B0031$-$07 \citep{McSweeney2019a}.
Aliasing can also ``amplify'' the variability of the drift rate if the ratio of stellar rotation and carousel rotation is very close to a ratio of small integers.
That is, a small change in the magnetospheric conditions (e.g. the local electromagnetic configuration) near the stellar surface (in the gap, where the sparks reside) can appear to the observer as a relatively large change in the drift rate.
\citet{VanLeeuwen2012} elucidated the connection between the accelerating potential within the polar gap and the carousel behavior, and found that the variability of B0826$-$34's drift rate can be explained in this way.
In contrast, \citet{VanLeeuwen2003} argued that aliasing could \emph{not} be present during the post-null changing drift rate for B0809$+$74.
Whether or not aliasing is included, models for changing drift rates are often discussed in terms of the local magnetospheric conditions changing over the relevant time scales \citep[e.g.][]{VanLeeuwen2003, Yuen2019}.
